---
title: "case3"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{R}
# Direction 1
# compute the equity strip yields at mid prices
# convert futures price to spot/strip price, Ptn = Ftn/e^(nytn)
dt1$spot12 <- dt1$F_t_12/exp(1*dt1$y_t_12)
dt1$spot24 <- dt1$F_t_24/exp(2*dt1$y_t_24)
dt1$spot36 <- dt1$F_t_36/exp(3*dt1$y_t_36)
dt1$spot48 <- dt1$F_t_48/exp(4*dt1$y_t_48)
dt1$spot60 <- dt1$F_t_60/exp(5*dt1$y_t_60)
dt1$spot72 <- dt1$F_t_72/exp(6*dt1$y_t_72)
dt1$spot84 <- dt1$F_t_84/exp(7*dt1$y_t_84)
# strip yields
dt1$yield12 <- (1/1)*log(dt1$div_12/dt1$spot12)
dt1$yield24 <- (1/2)*log(dt1$div_12/dt1$spot24)
dt1$yield36 <- (1/3)*log(dt1$div_12/dt1$spot36)
dt1$yield48 <- (1/4)*log(dt1$div_12/dt1$spot48)
dt1$yield60 <- (1/5)*log(dt1$div_12/dt1$spot60)
dt1$yield72 <- (1/6)*log(dt1$div_12/dt1$spot72)
dt1$yield84 <- (1/7)*log(dt1$div_12/dt1$spot84)
# construct the eighth column which is 7 year yeild minus 1 year yield at each date
dt1$yield7_1 <- dt1$yield84 - dt1$yield12

```

```{R}
# mean yield
m1 <- mean(dt1$yield12)
m2 <- mean(dt1$yield24)
m3 <- mean(dt1$yield36)
m4 <- mean(dt1$yield48)
m5 <- mean(dt1$yield60)
m6 <- mean(dt1$yield72)
m7 <- mean(dt1$yield84)
m8 <- mean(dt1$yield7_1)
# sd yield
sd1 <- sd(dt1$yield12)
sd2 <- sd(dt1$yield24)
sd3 <- sd(dt1$yield36)
sd4 <- sd(dt1$yield48)
sd5 <- sd(dt1$yield60)
sd6 <- sd(dt1$yield72)
sd7 <- sd(dt1$yield84)
sd8 <- sd(dt1$yield7_1)
```

```{R}
# mean of yield in a recession
dt1_recess <- subset(dt1, subset = recess==1)
r1 <- mean(dt1_recess$yield12)
r2 <- mean(dt1_recess$yield24)
r3 <- mean(dt1_recess$yield36)
r4 <- mean(dt1_recess$yield48)
r5 <- mean(dt1_recess$yield60)
r6 <- mean(dt1_recess$yield72)
r7 <- mean(dt1_recess$yield84)
r8 <- mean(dt1_recess$yield7_1)
# mean of yield not in recession
dt1_nonrecess <- subset(dt1, subset = recess==0)
nr1 <- mean(dt1_nonrecess$yield12)
nr2 <- mean(dt1_nonrecess$yield24)
nr3 <- mean(dt1_nonrecess$yield36)
nr4 <- mean(dt1_nonrecess$yield48)
nr5 <- mean(dt1_nonrecess$yield60)
nr6 <- mean(dt1_nonrecess$yield72)
nr7 <- mean(dt1_nonrecess$yield84)
nr8 <- mean(dt1_nonrecess$yield7_1)

```


```{R}
# Table 1: Strip Yields 4x8
Strip_Yields <- matrix(c(m1,m2,m3,m4,m5,m6,m7,m8,sd1,sd2,sd3,sd4,sd5,sd6,sd7,sd8,r1,r2,r3,r4,r5,r6,r7,r8,nr1,nr2,nr3,nr4,nr5,nr6,nr7,nr8),ncol=8,byrow=TRUE)
colnames(Strip_Yields) <- c("1 year", "2 year", "3 year", "4 year", "5 year", "6 year", "7 year", "7year - 1 year")
rownames(Strip_Yields) <- c("mean yield", "sd yield", "mean yield in recession", "mean yield outside recession")
Strip_Yields <- as.table(Strip_Yields)
Strip_Yields
```
Interpretation of Table1: 
Referring to the questions for report/presentation:
Q: Is the stripe yield curve upward sloping by maturity in this dataset? If the sample overrepresented recession, how would this impact the overall mean slope estiamte?
A:
   The overall yield curve is upward sloping for 1 year to 4 year, but then become slightly downward sloping from 4 year to 7 year.
   It seems that recession is overrepresented here and distoring the overall yield curve.
   If we seperate the dataset by in recession and outside recession, then we can clearly see that the yield curve is upward sloping outside recession and downward sloping in recession.
  
Q: Speculate on why strip yields might behave the way they do in recession and non-recession periods
A:
   Yield is high at the begining of the recession because investors are risk averse and demand higher return during time with high uncertainty.
   Also during recession, growth tends to slow down, leading to lower asset prices, thus higher yield, as they are inversely related.
   Recessions usually end after a few years, and as the economy warms up again, there will be less uncertainty and lower demand in return.
   Thus, the yield curve is downward sloping during recession.
   In contrast, outside recession, yield is originally low, and subtly increases as maturity increases, 
   primarily because higher uncertainty for longer maturity means higher maturity premium

```{R}
# Direction 2
# futures to spot price
dt2$spot0 <- dt2$F_t_0/exp(0*dt2$y_t_0)
dt2$spot11 <- dt2$F_t_11/exp((11/12)*dt2$y_t_11)
dt2$spot12 <- dt2$F_t_12/exp((12/12)*dt2$y_t_12)
dt2$spot23 <- dt2$F_t_23/exp((23/12)*dt2$y_t_23)
dt2$spot24 <- dt2$F_t_24/exp((24/12)*dt2$y_t_24)
dt2$spot35 <- dt2$F_t_35/exp((35/12)*dt2$y_t_35)
dt2$spot36 <- dt2$F_t_36/exp((36/12)*dt2$y_t_36)
dt2$spot47 <- dt2$F_t_47/exp((47/12)*dt2$y_t_47)
dt2$spot48 <- dt2$F_t_48/exp((48/12)*dt2$y_t_48)
dt2$spot59 <- dt2$F_t_59/exp((59/12)*dt2$y_t_59)
dt2$spot60 <- dt2$F_t_60/exp((60/12)*dt2$y_t_60)
dt2$spot71 <- dt2$F_t_71/exp((71/12)*dt2$y_t_71)
dt2$spot72 <- dt2$F_t_72/exp((72/12)*dt2$y_t_72)
dt2$spot83 <- dt2$F_t_83/exp((83/12)*dt2$y_t_83)
dt2$spot84 <- dt2$F_t_84/exp((84/12)*dt2$y_t_84)
# equity strip return
# 1 month - spot*(1+yield)/(last period spot) - 1 
dt2$r11 <- (dt2$spot11*(1+dt2$y_t_12)/dt2$spot12)-1
dt2$r23 <- (dt2$spot23*(1+dt2$y_t_24)/dt2$spot24)-1
dt2$r35 <- (dt2$spot35*(1+dt2$y_t_36)/dt2$spot36)-1
dt2$r47 <- (dt2$spot47*(1+dt2$y_t_48)/dt2$spot48)-1
dt2$r59 <- (dt2$spot59*(1+dt2$y_t_60)/dt2$spot60)-1
dt2$r71 <- (dt2$spot71*(1+dt2$y_t_72)/dt2$spot72)-1
dt2$r83 <- (dt2$spot83*(1+dt2$y_t_84)/dt2$spot84)-1
# 1 year
dt2$r12 <- (dt2$spot0*(1+dt2$y_t_12)/dt2$spot12)-1
dt2$r24 <- (dt2$spot12*(1+dt2$y_t_24)/dt2$spot24)-1
dt2$r36 <- (dt2$spot24*(1+dt2$y_t_36)/dt2$spot36)-1
dt2$r48 <- (dt2$spot36*(1+dt2$y_t_48)/dt2$spot48)-1
dt2$r60 <- (dt2$spot48*(1+dt2$y_t_60)/dt2$spot60)-1
dt2$r72 <- (dt2$spot60*(1+dt2$y_t_72)/dt2$spot72)-1
dt2$r84 <- (dt2$spot72*(1+dt2$y_t_84)/dt2$spot84)-1
# 7-1 column
dt2$r7_1_1 <- dt2$r83-dt2$r11
dt2$r7_1_12 <- dt2$r84-dt2$r12

```

```{R}
# annualized mean monthly return
amr1 <- mean(dt2$r11)*12
amr2 <- mean(dt2$r23)*12
amr3 <- mean(dt2$r35)*12
amr4 <- mean(dt2$r47)*12
amr5 <- mean(dt2$r59)*12
amr6 <- mean(dt2$r71)*12
amr7 <- mean(dt2$r83)*12
amr8 <- mean(dt2$r7_1_1)*12
# annualized standard deviation of monthly return
asd1 <- sd(dt2$r11)*sqrt(12)
asd2 <- sd(dt2$r23)*sqrt(12)
asd3 <- sd(dt2$r35)*sqrt(12)
asd4 <- sd(dt2$r47)*sqrt(12)
asd5 <- sd(dt2$r59)*sqrt(12)
asd6 <- sd(dt2$r71)*sqrt(12)
asd7 <- sd(dt2$r83)*sqrt(12)
asd8 <- sd(dt2$r7_1_1)*sqrt(12)
# annaulized Sharpe Ratio for monthly return
asr1 <- (amr1-mean(dt2$y_t_12))/asd1
asr2 <- (amr2-mean(dt2$y_t_24))/asd2
asr3 <- (amr3-mean(dt2$y_t_36))/asd3
asr4 <- (amr4-mean(dt2$y_t_48))/asd4
asr5 <- (amr5-mean(dt2$y_t_60))/asd5
asr6 <- (amr6-mean(dt2$y_t_72))/asd6
asr7 <- (amr7-mean(dt2$y_t_84))/asd7
asr8 <- (amr8-(mean(dt2$y_t_84)-mean(dt2$y_t_12)))/asd8

```

```{R}
# mean 12 month return
ayr1 <- mean(dt2$r12)
ayr2 <- mean(dt2$r24)
ayr3 <- mean(dt2$r36)
ayr4 <- mean(dt2$r48)
ayr5 <- mean(dt2$r60)
ayr6 <- mean(dt2$r72)
ayr7 <- mean(dt2$r84)
ayr8 <- mean(dt2$r7_1_12)
# standard deviation of 12month return
ysd1 <- sd(dt2$r12)
ysd2 <- sd(dt2$r24)
ysd3 <- sd(dt2$r36)
ysd4 <- sd(dt2$r48)
ysd5 <- sd(dt2$r60)
ysd6 <- sd(dt2$r72)
ysd7 <- sd(dt2$r84)
ysd8 <- sd(dt2$r7_1_12)
# Sharpe Ratio for 12 month return
ysr1 <- (ayr1-mean(dt2$y_t_12))/ysd1
ysr2 <- (ayr2-mean(dt2$y_t_24))/ysd2
ysr3 <- (ayr3-mean(dt2$y_t_36))/ysd3
ysr4 <- (ayr4-mean(dt2$y_t_48))/ysd4
ysr5 <- (ayr5-mean(dt2$y_t_60))/ysd5
ysr6 <- (ayr6-mean(dt2$y_t_72))/ysd6
ysr7 <- (ayr7-mean(dt2$y_t_84))/ysd7
ysr8 <- (ayr8-(mean(dt2$y_t_84)-mean(dt2$y_t_12)))/ysd8

```

```{R}
# Table 2: Strip Returns
Strip_Returns <- matrix(c(amr1,amr2,amr3,amr4,amr5,amr6,amr7,amr8,asd1,asd2,asd3,asd4,asd5,asd6,asd7,asd8,asr1,asr2,asr3,asr4,asr5,asr6,asr7,asr8,
                          ayr1,ayr2,ayr3,ayr4,ayr5,ayr6,ayr7,ayr8,ysd1,ysd2,ysd3,ysd4,ysd5,ysd6,ysd7,ysd8,ysr1,ysr2,ysr3,ysr4,ysr5,ysr6,ysr7,ysr8),ncol=8,byrow=TRUE)
colnames(Strip_Returns) <- c("1 year", "2 year", "3 year", "4 year", "5 year", "6 year", "7 year", "7year - 1 year")
rownames(Strip_Returns) <- c("annualized mean monthly return", "annualized sd of monthly return", "annualized Sharpe Ratio of monthly return",
                             "mean 12 month return","sd of 12 month return", "Sharpe Ratio of 12 month return")
Strip_Returns <- as.table(Strip_Returns)
Strip_Returns

```
Interpretation of Table 2:

  Holding period returns tend to be rising with maturity in this dataset, so do the Sharpe Ratios
  
  Higher holding period returns for long maturity are likely result of maturity premium and liquidity premium for longer maturity products.
  Meaning that market participants anticipate higher uncertainty with long maturity.
  Therefore, long maturity strip contracts are relatively riskier than short maturity ones.


```{R}
# Direction 3: bid-ask spread
# bid-ask spread based on formula on case document
dt3$ba1 <- (dt3$F.ask_t_12-dt3$F.bid_t_12)/(0.5*(dt3$F.ask_t_12+dt3$F.bid_t_12))
dt3$ba2 <- (dt3$F.ask_t_24-dt3$F.bid_t_24)/(0.5*(dt3$F.ask_t_24+dt3$F.bid_t_24))
dt3$ba3 <- (dt3$F.ask_t_36-dt3$F.bid_t_36)/(0.5*(dt3$F.ask_t_36+dt3$F.bid_t_36))
dt3$ba4 <- (dt3$F.ask_t_48-dt3$F.bid_t_48)/(0.5*(dt3$F.ask_t_48+dt3$F.bid_t_48))
dt3$ba5 <- (dt3$F.ask_t_60-dt3$F.bid_t_60)/(0.5*(dt3$F.ask_t_60+dt3$F.bid_t_60))
dt3$ba6 <- (dt3$F.ask_t_72-dt3$F.bid_t_72)/(0.5*(dt3$F.ask_t_72+dt3$F.bid_t_72))
dt3$ba7 <- (dt3$F.ask_t_84-dt3$F.bid_t_84)/(0.5*(dt3$F.ask_t_84+dt3$F.bid_t_84))
# mean spread for each maturity
ms1 <- mean(dt3$ba1)
ms2 <- mean(dt3$ba2)
ms3 <- mean(dt3$ba3)
ms4 <- mean(dt3$ba4)
ms5 <- mean(dt3$ba5)
ms6 <- mean(dt3$ba6)
ms7 <- mean(dt3$ba7)
# sd for bid-ask spread
sds1 <- sd(dt3$ba1)
sds2 <- sd(dt3$ba2)
sds3 <- sd(dt3$ba3)
sds4 <- sd(dt3$ba4)
sds5 <- sd(dt3$ba5)
sds6 <- sd(dt3$ba6)
sds7 <- sd(dt3$ba7)
# mean spread recession
dt3_recess <- subset(dt3, subset = recess==1)
msr1 <- mean(dt3_recess$ba1)
msr2 <- mean(dt3_recess$ba2)
msr3 <- mean(dt3_recess$ba3)
msr4 <- mean(dt3_recess$ba4)
msr5 <- mean(dt3_recess$ba5)
msr6 <- mean(dt3_recess$ba6)
msr7 <- mean(dt3_recess$ba7)
# mean spread non-recession
dt3_nonrecess <- subset(dt3, subset = recess==0)
msnr1 <- mean(dt3_nonrecess$ba1)
msnr2 <- mean(dt3_nonrecess$ba2)
msnr3 <- mean(dt3_nonrecess$ba3)
msnr4 <- mean(dt3_nonrecess$ba4)
msnr5 <- mean(dt3_nonrecess$ba5)
msnr6 <- mean(dt3_nonrecess$ba6)
msnr7 <- mean(dt3_nonrecess$ba7)
```

```{R}
# Table 3: Bid Ask Spreads
Bid_Ask_Spreads <- matrix(c(ms1,ms2,ms3,ms4,ms5,ms6,ms7,
                            sds1,sds2,sds3,sds4,sds5,sds6,sds7,
                            msr1,msr2,msr3,msr4,msr5,msr6,msr7,
                            msnr1,msnr2,msnr3,msnr4,msnr5,msnr6,msnr7),ncol=7,byrow=TRUE)
colnames(Bid_Ask_Spreads) <- c("1 year", "2 year", "3 year", "4 year", "5 year", "6 year", "7 year")
rownames(Bid_Ask_Spreads) <- c("mean spread", "standard deviation", "mean spread during recession","mean spread outside recession")
Bid_Ask_Spreads <- as.table(Bid_Ask_Spreads)
Bid_Ask_Spreads
```
Interpretation of Table 3:

  Bid-ask spread will reduce holding period return because the ask price is always higher than the bid price.
  Bid-ask spread tend to rise with maturity, indicating that long maturity strip contracts are less liquid.
  Spreads tend to be higher for all maturity / investment horizon during recession, likely a result of increase uncertainty in market and less liquidity during recession.


```{R}
# Direction 4: Spread adjusted returns
SAR11 <- (dt3$F.bid_t_11*(1+dt2$y_t_12)/dt3$F.ask_t_12)*(exp(-(11/12-1)*dt2$y_t_11) / exp(-(1)*dt2$y_t_12))-1
SAR23 <- (dt3$F.bid_t_23*(1+dt2$y_t_24)/dt3$F.ask_t_24)*(exp(-(23/12-1)*dt2$y_t_23) / exp(-(2)*dt2$y_t_24))-1
SAR35 <- (dt3$F.bid_t_35*(1+dt2$y_t_36)/dt3$F.ask_t_36)*(exp(-(35/12-1)*dt2$y_t_35) / exp(-(3)*dt2$y_t_36))-1
SAR47 <- (dt3$F.bid_t_47*(1+dt2$y_t_48)/dt3$F.ask_t_48)*(exp(-(47/12-1)*dt2$y_t_47) / exp(-(4)*dt2$y_t_48))-1
SAR59 <- (dt3$F.bid_t_59*(1+dt2$y_t_60)/dt3$F.ask_t_60)*(exp(-(59/12-1)*dt2$y_t_59) / exp(-(5)*dt2$y_t_60))-1
SAR71 <- (dt3$F.bid_t_71*(1+dt2$y_t_72)/dt3$F.ask_t_72)*(exp(-(71/12-1)*dt2$y_t_71) / exp(-(7)*dt2$y_t_72))-1
SAR83 <- (dt3$F.bid_t_83*(1+dt2$y_t_84)/dt3$F.ask_t_84)*(exp(-(83/12-1)*dt2$y_t_83) / exp(-(8)*dt2$y_t_84))-1
SAR83_11 <- SAR83-SAR11
#12-month
SAR12 <- (dt3$F.bid_t_12*(1+dt2$y_t_0)/dt3$F.ask_t_12)*(exp(-(12/12-1)*dt2$y_t_11)  / exp(-(1)*dt2$y_t_12))-1
SAR24 <- (dt3$F.bid_t_24*(1+dt2$y_t_12)/dt3$F.ask_t_24)*(exp(-(24/12-1)*dt2$y_t_11) / exp(-(2)*dt2$y_t_12))-1
SAR36 <- (dt3$F.bid_t_36*(1+dt2$y_t_24)/dt3$F.ask_t_36)*(exp(-(36/12-1)*dt2$y_t_11) / exp(-(3)*dt2$y_t_12))-1
SAR48 <- (dt3$F.bid_t_48*(1+dt2$y_t_36)/dt3$F.ask_t_48)*(exp(-(48/12-1)*dt2$y_t_11) / exp(-(4)*dt2$y_t_12))-1
SAR60 <- (dt3$F.bid_t_60*(1+dt2$y_t_48)/dt3$F.ask_t_60)*(exp(-(60/12-1)*dt2$y_t_11) / exp(-(5)*dt2$y_t_12))-1
SAR72 <- (dt3$F.bid_t_72*(1+dt2$y_t_60)/dt3$F.ask_t_72)*(exp(-(72/12-1)*dt2$y_t_11) / exp(-(6)*dt2$y_t_12))-1
SAR84 <- (dt3$F.bid_t_84*(1+dt2$y_t_72)/dt3$F.ask_t_84)*(exp(-(84/12-1)*dt2$y_t_11) / exp(-(7)*dt2$y_t_12))-1
SAR84_12 <- SAR84 - SAR12
```

```{R}
#Annualized monthly SAR
ASAR1 <- mean(SAR11)*12
ASAR2 <- mean(SAR23)*12
ASAR3 <- mean(SAR35)*12
ASAR4 <- mean(SAR47)*12
ASAR5 <- mean(SAR59)*12
ASAR6 <- mean(SAR71)*12
ASAR7 <- mean(SAR83)*12
ASAR8 <- mean(SAR83_11)*12
#Annualized SD SAR
SDSAR1 <- sd(SAR11)*sqrt(12)
SDSAR2 <- sd(SAR23)*sqrt(12)
SDSAR3 <- sd(SAR35)*sqrt(12)
SDSAR4 <- sd(SAR47)*sqrt(12)
SDSAR5 <- sd(SAR59)*sqrt(12)
SDSAR6 <- sd(SAR71)*sqrt(12)
SDSAR7 <- sd(SAR83)*sqrt(12)
SDSAR8 <- sd(SAR83_11)*sqrt(12)
#Annualized Sharpe Ratio
ASAR_SR1 <- (ASAR1-mean(dt2$y_t_12))/ SDSAR1
ASAR_SR2 <- (ASAR2-mean(dt2$y_t_24))/ SDSAR2
ASAR_SR3 <- (ASAR3-mean(dt2$y_t_36))/ SDSAR1
ASAR_SR4 <- (ASAR4-mean(dt2$y_t_48))/ SDSAR1
ASAR_SR5 <- (ASAR5-mean(dt2$y_t_60))/ SDSAR1
ASAR_SR6 <- (ASAR6-mean(dt2$y_t_72))/ SDSAR1
ASAR_SR7 <- (ASAR7-mean(dt2$y_t_84))/ SDSAR1
ASAR_SR8 <- (ASAR8-mean(dt2$y_t_84)-mean(dt2$y_t_12))/ SDSAR8
```


```{R}
#mean 12 month return
m12 <- mean(SAR12)
m24 <- mean(SAR24)
m36 <- mean(SAR36)
m48 <- mean(SAR48)
m60 <- mean(SAR60)
m72 <- mean(SAR72)
m84 <- mean(SAR84)
m84_12 <- mean(SAR84_12)
#SD of 12 month return
sd12 <- sd(SAR12)
sd24 <- sd(SAR24)
sd36 <- sd(SAR36)
sd48 <- sd(SAR48)
sd60 <- sd(SAR60)
sd72 <- sd(SAR72)
sd84 <- sd(SAR84)
sd84_12 <- sd(SAR84_12)
#Sharpe 12 month return
SR12 <- (m12-mean(dt2$y_t_12))/sd12
SR24 <- (m24-mean(dt2$y_t_24))/sd24
SR36 <- (m36-mean(dt2$y_t_36))/sd36
SR48 <- (m48-mean(dt2$y_t_48))/sd48
SR60 <- (m60-mean(dt2$y_t_60))/sd60
SR72 <- (m72-mean(dt2$y_t_72))/sd72
SR84 <- (m84-mean(dt2$y_t_84))/sd84
SR84_12 <- (m84_12-mean(dt2$y_t_84)- mean(dt2$y_t_12))/sd84_12
```

```{r}
four_matrix <- matrix(c(ASAR1, ASAR2, ASAR3, ASAR4, ASAR5, ASAR6, ASAR_SR7, ASAR_SR8,
                        SDSAR1, SDSAR2, SDSAR3, SDSAR4, SDSAR5, SDSAR6, SDSAR7, SDSAR8,
                        ASAR_SR1, ASAR_SR2, ASAR_SR3, ASAR_SR4, ASAR_SR5, ASAR_SR6, ASAR_SR7, ASAR_SR8,
                        m12, m24, m36, m48, m60, m72, m84, m84_12,
                        sd12, sd24, sd36, sd48, sd60, sd72, sd84, sd84_12,
                        SR12, SR24, SR36, SR48, SR60, SR72, SR84, SR84_12), ncol = 8, byrow = TRUE)
colnames(four_matrix) <- c("1 year", "2 year", "3 year", "4 year", "5 year", "6 year", "7 year", "7-1")
rownames(four_matrix) <- c("Annualized SA Ret", "Annualized SA Std. Dev.", "Annualized SA Sharpe", "Mean 12-month Ret", "12-month Std. dev.", "12-month Sharpe")
four_table <- as.table(four_matrix)
four_table

```


```{R}
# Direction 5: 

```


```{r}
library(dplyr)
es_returns_1 <- matrix(ncol = 7, nrow = length(dt2$spot0))
for(i in 1:7) {
   es_returns_1[,i] <- lead(dt2[,paste("dt3$F.ask_t_11", i*11-1, sep = "")])/(dt2[,paste("dt3$F.bid_t_11", i*12, sep = "")]) -1 
}



```
```{r}
library(dplyr)
mean_free_1 <- c()
for (i in 1:7) {
  mean_free_1 <- c(mean_free_1, mean(dt2[, paste("y_t_",i*12,sep="")], na.rm=TRUE))
}
mean_free_1 <- c(mean_free_1, mean_free_1[7] - mean_free_1[1])
mean_free_12 <- c()
for (i in 1:7) {
  mean_free_12 <- c(mean_free_12, mean(dt2[, paste("y_t_",i*12,sep="")], na.rm=TRUE))
}
mean_free_12 <- c(mean_free_12, mean_free_12[7] - mean_free_12[1])
return_func = matrix(ncol=7,nrow=length(dt3$F.bid_t_0))
for (i in 1:7) {
  x_f = lead(dt3[,paste("F.bid_t_",i*11+i-1, sep="")])/(dt3[,paste("F.ask_t_",i*12, sep="")])
  temp = exp(-(i*11+i-1)*lead(dt2[,paste("y_t_",i*11+i-1,sep="")]))/exp(-i*12*dt2[,paste("y_t_",i*12,sep="")])
  return_func[,i] = x_f * temp - 1
}
return_func_1 = matrix(ncol=7,nrow=length(dt3$F.bid_t_0))
for (i in 1:7) {
  x_f_1 = lead(dt3[,paste("F.bid_t_",i*12-12, sep="")],12)/(dt3[,paste("F.ask_t_",i*12, sep="")])
  temp_1 = exp(-(i*12-12)*lead(dt2[,paste("y_t_",i*12-12,sep="")],12))/exp(-i*12*dt2[,paste("y_t_",i*12,sep="")])
  return_func_1[,i] = x_f_1 * temp_1 -1 
}
spread_mean = colMeans(return_func, na.rm=TRUE)
spread_mean = c(spread_mean, spread_mean[7]-spread_mean[1])
spread_sd = apply(return_func, 2, sd,na.rm=TRUE)
spread_sd = c(spread_sd, spread_sd[7]-spread_sd[1])
spread_sr = (spread_mean - mean_free_1)/spread_sd
spread_mean_1 = colMeans(return_func_1, na.rm=TRUE)
spread_mean_1 = c(spread_mean_1, spread_mean_1[7]-spread_mean_1[1])
spread_sd_1 = apply(return_func_1, 2, sd, na.rm=TRUE)
spread_sd_1 = c(spread_sd_1, spread_sd_1[7]-spread_sd_1[1])
spread_sr_1 = (spread_mean_1 - mean_free_12)/spread_sd_1
```

```{r}
# Table 4: Spread Adjusted Strip Returns.
Table_4 <- rbind(spread_mean, spread_sd, spread_sr, spread_mean_1, spread_sd_1, spread_sr_1)
colnames(Table_4) <- c("1 Year","2 Years", "3 Years", "4 Years","5 Years", "6 Years","7 Years","Yr 7 to 1 Diff")
Table_4



```

