---
title: "McLemore Logit"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
rm(list = ls())
```


```{r cars}
library(e1071)
library(rpart)
## nonlinear svm
library(lattice)
library(caret)
#Test Model performance
#install.packages("ROCR")
library("ROCR")
#install.packages("naniar")
library(naniar)
library(caret)
library(regclass)
#install.packages("ggthemr")
library(broom)
library(grid)
library(gridExtra)
library(scales)
library(ggthemes)
library(data.table)
library(janitor)
library(stringr)
library(PerformanceAnalytics)
library(corrplot)
install.packages("plotfunctions")
library(plotfunctions)
library(ggpubr)
install.packages("logistf")
install.packages("mlbench")
install.packages("cutpointr")
library(logistf)
library(car)
library(MASS)
library(dplyr)
library(mlbench)
library(tidyverse)
library(cutpointr)
```

```{r pressure, echo=FALSE}
#read in data
#getwd()

BI <- read.csv("BI_CommunityInvestment_contacts.csv")
HS <- read.csv("HS_CommunityInvsestment_Contacts.csv")

nrow(BI)
```

```{r}
#####
#Cleaning
#####
#clean column headers
BI <- clean_names(BI)
HS <- clean_names(HS)

str(BI) 
#create & Close date needs to be in date format
BI$i_createdate <- as.Date(BI$i_createdate)
BI$closedate <- as.Date(BI$closedate)


#fisrt_marketing_email needs date format
HS$fisrt_marketing_email <- as.Date(HS$fisrt_marketing_email, format = "%Y-%m-%d")

#concatenate first and last name
HS$name <- paste(HS$first_name, HS$last_name)
nrow(BI)
```


```{r}
#fix BI$dealname
BI_name <- BI$dealname
BI_name <- str_remove(BI_name, "	- ")
BI_name <- str_remove(BI_name, "- " )
BI_name <- str_remove(BI_name, "-")
BI_name <- str_remove(BI_name, "	  ")
BI_name <- str_remove(BI_name, " Deal") 
BI_name <- str_remove(BI_name, "CI Deal") 
BI_name <- str_remove(BI_name, "MCL-Deal")
BI_name <- str_remove(BI_name, "MCLDeal")
BI_name <- str_remove(BI_name, "MCL--")
BI_name <- str_remove(BI_name, "MCL-")
BI_name <- str_remove(BI_name, "NewDeal ")
BI_name <- str_remove(BI_name, "NewDeal")
BI_name <- str_remove(BI_name," - New Deal")
BI_name <- str_remove(BI_name,"New")
BI_name <- str_remove(BI_name, ", FAIA, FACHA")
BI_name <- str_remove(BI_name, " ()")
BI_name <- str_remove(BI_name, " ")
BI_name <- str_remove(BI_name, "McL CI -")
BI_name <- str_remove(BI_name, "MCL CI ")
BI_name <- str_remove(BI_name, "MCLCI")
BI_name <- str_remove(BI_name, "McLCI")
BI_name <- str_remove(BI_name, "McL CI Deal  - ")
BI_name <- str_remove(BI_name, " - CI Deal")
BI_name <- str_remove(BI_name, " - CI Deal")
BI_name <- str_remove(BI_name, "CI")
BI_name <- str_remove(BI_name, " ")


BI_name <- trimws(BI_name)
BI_name[30:53] <- gsub('  ', '', BI_name[30:53])
BI_name <- gsub('  ', '', BI_name)

#specific names
BI_name[200] <- "Jeff Glowacki"
BI_name[228] <- "John Thomas"
BI_name[19] <- "Kevin Guarino"
BI_name[20] <- "Michael Straw"
BI_name[26] <- "Allen Hill"
BI_name[62] <- "Andrew McCoy"
BI_name[65] <- "B.W. Franks"
BI_name[103] <- "Charles McDowell"
BI_name[113] <- "Chris Peck"
BI_name[1] <- "Allen Rogers"
BI_name[100] <- "Chadwick Wallace"
BI_name[210] <- "Jessica Dietrich Marsh"
BI_name[349] <- "Sam Horner"
BI_name[303] <- "Jon Sheumack"
BI_name[421] <- "Mike McDaniel"
BI_name[293] <- "Michel Leaughlin"
BI_name[425] <- "Roger Marks"
BI_name[23] <- "Shayne  McCallie"
BI_name[273] <- "Mark League"
BI_name[334] <- "Rob LeFever"
BI_name[371] <- "Steve Husome"
BI_name[385] <- "Terry DeWitt"
BI_name[395] <- "Todd McClure"
BI_name[304] <- "Nathan DuMond"
BI_name[403] <- "Tommy McClelland"
BI_name[409] <- "Wallace Michael and Regina"
BI_name[20] <- "Michael Straw"


#Separate first and last names with no spaces
BI_name <- gsub('([[:upper:]])', ' \\1', BI_name)
BI_name <- trimws(BI_name)

BI_name[1:53] <- gsub('([[:upper:]])', ' \\1', BI_name[1:53])
BI_name[420:430] <- gsub('([[:upper:]])', ' \\1', BI_name[420:430])
BI_name[420:430] <- trimws(BI_name[423:430])


#test 1
nchar(BI_name)[2]#correct
nchar(BI_name)[430]
BI_name[1] <- gsub('([[:upper:]])', ' \\1', BI_name[1])

#remove extra space
BI_name <- gsub("\\s+"," ",BI_name)
BI_name[23] <- gsub("\\s+"," ",BI_name[23])   #Bob Harrison
BI_name[3:53] <- gsub("\\s+"," ",BI_name[3:53])
BI_name[3:17] <- gsub("\\s+"," ",BI_name[3:17])
BI_name[2:25] <- gsub("\\s+"," ",BI_name[2:25])

View(BI_name)

#Append the name vector back into BI
BI <- cbind(BI, BI_name)

```

```{r}
#look at the HS$name column
View(HS$name)

HS$name[246] <- "Steve Husome"
HS$name[283] <- "William Ryan"
HS$name[192] <- "Mike Mcdaniel"
HS$name[80] <- "Frank McPhearson"
HS$name[139] <- "John Thomas"
HS$name[159] <- "Kenneth Engelsmann"

```


```{r}
#merge the datasets based on name
nrow(BI)
nrow(HS)
HSBI <- merge(BI, HS, by.x = "BI_name",by.y = "name")

```

```{r}
#delete columns
colnames(HSBI)
HSBI <- HSBI[, -c(12,13)]  #remove duplicated name columns

```

```{r}
#summary(HSBI) #the summary statistics makes since for each column

#create prediction column from close date
HSBI$CloseWon <- c()

for (i in 1:nrow(HSBI)) {
  if (is.na(HSBI$closedate[i])) {
    HSBI$CloseWon[i] <- 0
} else {
    HSBI$CloseWon[i] <- 1  
}
}

head(HSBI)
```

```{r}
#change data type to numeric
HSBI$CloseWon <- as.numeric(HSBI$CloseWon)
#check proportion of deals are won or lost
mean(HSBI$CloseWon)  #~52% of observations are closed won
```
```{r}
#check missing values
gg_miss_var(HSBI)  #mostly not an issue
#sum(is.na(HSBI$number_of_times_contacted)) #1
#sum(is.na(HSBI$number_of_sales_activities)) #1

```

```{r}
##############
#Exploratory Data Analysis
#str(HSBI)

#plot distributions of numeric data
#days to close
#number of time contcted
#number of sales activities
#average pageviews
#marketing emails delivered
#Number of unique forms submitted

#below is a dataframe that removes all lost deals
HSBI.CW <- filter(HSBI, CloseWon == 1)

ggarrange(
ggplot(data = HSBI.CW, mapping = aes(x = days_to_close, y = ..density..)) + geom_histogram(binwidth = 10, color = "black", fill = "white", boundary = 0),
ggplot(data = HSBI, mapping = aes(x = number_of_times_contacted, y = ..density..)) + geom_histogram(binwidth = 1, color = "black", fill = "white",boundary = 1),
ggplot(data = HSBI, mapping = aes(x = number_of_sales_activities, y = ..density..)) + geom_histogram(binwidth = 2, color = "black", fill = "white",boundary = 1),
ggplot(data = HSBI, mapping = aes(x = average_pageviews, y = ..density..)) + geom_histogram(binwidth = 1, color = "black", fill = "white",boundary = 0),
ggplot(data = HSBI, mapping = aes(x = marketing_emails_delivered, y = ..density..)) + geom_histogram(binwidth = 2, color = "black", fill = "white",boundary = 1),
ggplot(data = HSBI, mapping = aes(x = number_of_unique_forms_submitted, y = ..density..)) + geom_histogram(binwidth = 1, color = "black", fill = "white",boundary = 1), 
ncol = 3, nrow = 2)


```

```{r}
#Proportion of Closed Won vs. Lost based on specific variables
par(mfrow = c(2,1))
plot(factor(CloseWon) ~ factor(number_of_times_contacted), data=HSBI, col=c(2,9), ylab="Closed Won Rate", xlab = "Number of Times Contacted")
plot(factor(CloseWon) ~ factor(marketing_emails_delivered), data=HSBI, col=c(2,9), ylab="Closed Won Rate", xlab = "Marketing Emails Delivered")
```


```{r}
#State
plot(factor(CloseWon) ~ factor(state), data = HSBI, col = c(2,9), ylab = "Closed Won Rate", cex.names = 0.5)
```


```{r}
#Original Source
plot(factor(CloseWon) ~ factor(original_source), data = HSBI, col = c(2,9), ylab = "Closed Won Rate", xlab =  "Original Source")

```


```{r}
#filter out close lost deals
HSBI.CW <- filter(HSBI, CloseWon == 1)
#boxplot of days to close by state
#Of all deals that closed won, NY, IL, CO, CA, VA were the shorted time to close by looking at the median time
ggplot(data = HSBI.CW, aes(x = factor(state), y = days_to_close)) + geom_boxplot()
ggplot(data = HSBI, aes(x =number_of_times_contacted, y = days_to_close)) + geom_point()
```


```{r}
#plot days to close by contact owner
#shawn seems to get deals closed quicker
ggarrange(
ggplot(data = HSBI.CW, aes(x = factor(contact_owner), y = days_to_close)) + geom_boxplot() + labs(title = "Days to Close By Deal Owner"), 

#cannot determine whether someone is taking more time to close due to 
# number of times contacted, or visa versa.


ggplot(data = HSBI, aes(x =original_source, y = average_pageviews)) + geom_boxplot() + labs(title = "Page Views by Source Marketing"),

#look at of closed won deals, which ones were quicker 
# to close based on marketing source
ggplot(data = HSBI.CW, aes(x =original_source, y = days_to_close)) + geom_boxplot() + labs(title = "Days to Close by Source Marketing"),

ncol = 3, nrow = 1)


```

```{r}
#group by to get percent of won deals by state
#HSBI.CW %>% group_by(state) %>% summarise(sum(CloseWon)) 
```

```{r}
#split data into test/train
all <- 1:nrow(HSBI)
train <- sort(sample(1:nrow(HSBI), round(nrow(HSBI)*0.75, digits = 0), replace=FALSE))
test <- all[-train]

HSBI_train <- HSBI[train, ]
HSBI_test <- HSBI[test, ]

```

```{r}
#logit Model 1
mod.glm <- glm(CloseWon ~ factor(state) + number_of_times_contacted + number_of_sales_activities + factor(original_source) + average_pageviews + marketing_emails_delivered + sends_since_last_engagement, data = HSBI_train, family = "binomial")

```

```{r}
#print Summary output
summary(mod.glm)
```

```{r}
#plot residuals of model vs. all predictors
#plots should show no trend other than horizontal line.
#any trend indicates there is a relationship between 
#residuals and predictor

#number of times contacted and number of sales activities may require a transformation
residualPlots(mod.glm)

```

We pass the training set into the rfe algorithm to allow for recursive feature selection. The result will provide an optimal model based on minimizing the RMSE 
```{r}
#feature selection

#RFE cannot read in NA values
HSBI_train$number_of_sales_activities[is.na(HSBI_train$number_of_sales_activities)] <- 0
HSBI_train$number_of_times_contacted[is.na(HSBI_train$number_of_times_contacted)] <- 0

sum(is.na(HSBI_train$number_of_times_contacted))
sum(is.na(HSBI_train$number_of_sales_activities))

control <- rfeControl(functions = rfFuncs, method = "cv", number = 10)
rfe <- rfe(HSBI_train[,c(13,16,17,19,20,21,26)], HSBI_train[,30], sizes = c(1:7), rfeControl = control)
```


```{r}
#get table
print(rfe)
```

#4 variables is the optimal model including: "marketing_emails_delivered"  "number_of_times_contacted"   "number_of_sales_activities"  "sends_since_last_engagement"
```{r}
#get predictors
rfe$optVariables

#plots the number of variables with reduction function on y-axis
plot(rfe, type = c("g", "o"))
```
Although the optimal model includes 4 variables, we see a higher psudo R^2 with the original model call.

```{r}
#nulmodel
nullmod <- glm(CloseWon ~ 1, data = HSBI_train, family = "binomial")

#pseudo R-squarred
1-logLik(mod.glm) / logLik(nullmod)
#1-logLik(mod.opt) / logLik(nullmod)
```

```{r}
#run optimal model based on RFE output
mod.opt <- glm(CloseWon ~ marketing_emails_delivered + number_of_sales_activities + number_of_times_contacted + sends_since_last_engagement, data = HSBI_train, family = "binomial")

summary(mod.opt)

```
```{r}
#predict the optimal model
pred.opt <- predict(mod.opt, HSBI_test, type = "response")


#Length of test set is not ideal
nrow(HSBI_test)
```
```{r}
#setup dataframe with predictions values and actuals for visuals
cmdf <- data.frame(pred.opt, HSBI_test$CloseWon)
cmdf$pred.opt <- round(cmdf$pred.opt,4)

table(ifelse(cmdf$pred.opt>0.5, "1", "0"))
table(cmdf$HSBI_test.CloseWon)



cm <- confusionMatrix(as.factor(ifelse(cmdf$pred.opt>0.50, 1, 0)), as.factor(cmdf$HSBI_test.CloseWon))
# Accuracy = 65% with cuttoff at .5
cm
```
The accuracy is ~65% TN+TP/(TN+TP+FN+FP); however, the p-value fails. The overall accuracy rate is not greater than than the proportion of the largest class in the test set according to p-value. 

We would like to see more data in the test set

```{r}
#create for loop for confusion matrix types for plotting
cmdf$type <- ""
#cutoff = 50%
# for (i in 1:nrow(cmdf)) {
#   if (cmdf$pred.opt[i] >= 0.5 & cmdf$HSBI_test.CloseWon[i] == 1)
#     cmdf$type[i] <- "TP"
#   else if (cmdf$pred.opt[i] >= 0.5 & cmdf$HSBI_test.CloseWon[i] == 0)
#     cmdf$type[i] <- "FP"
#   else if (cmdf$pred.opt[i] < 0.5 & cmdf$HSBI_test.CloseWon[i] == 1)
#     cmdf$type[i] <- "FN"
#   else if (cmdf$pred.opt[i] < 0.5 & cmdf$HSBI_test.CloseWon[i] == 0)
#     cmdf$type[i] <- "TN"
#   else (cmdf$pred.opt[i] <- "NA")
# }
```


```{r}
#plot the confusion matrix result type 
ggplot(data = cmdf, aes(x = HSBI_test.CloseWon,y = pred.opt, color = type)) + geom_point(alpha = 0.25, size = 0.05) + geom_jitter() + geom_hline(yintercept = .5, color = "black") + labs(title = "Confusion Matrix Results, Cutoff = 0.5", x = 'Predicted', y = 'Actual')

```



Below shows no observable trend between the independent variables in the optimized model and the residuals.

```{r}
#Test for Relationship with covariates and model residuals
#No predictor shows a trend with the residuals
residualPlots(mod.opt) 
```



